Adaptive evolution with aneuploidy and mutation

### 2022-06-19 ms/ms.tex
updated plots with truncated kde and organized results files and notebooks

After producing a set of weighted particles from the the posterior distribution using the above ABC-SMC algorithm, we approximate the posterior using kernel density estimation (KDE) with Gaussian kernels, from which we find the MAP (maximum a posteriori) estimate as the maximum of the KDE function. We then draw $50,000$ samples from the posterior KDE to compute the HDI (highest density interval) and visualize the posterior distribution with histograms.

>>>>

After producing a set of weighted particles from the the posterior distribution using the above ABC-SMC algorithm, we approximate the posterior using kernel density estimation (KDE) with Gaussian kernels. Since KDE can have positive posterior probability for values with the prior zero, we truncate KDE, giving zero probability for the ranges outside of the prior. From maximum of the KDE function we get the MAP (maximum a posteriori) estimate, and then draw $5,000,000$ samples from the posterior KDE to compute the HDI (highest density interval) and draw $50,000$ samples from it to visualize the posterior distribution with histograms.
